A Bioconductor workflow for processing and analysing spatial proteomics data

### 2018-04-17 bioc-workflow-resubmit.tex
changes until sml, with travis condif update

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{hl}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 5032 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData: none
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2R6 (5032 total)
##   fvarLabels: X X.1 ... Cell.Surface.Proteins (25 total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
## Annotation:  
## - - - Processing information - - -
##  MSnbase version: 2.5.12
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{combined} \hlkwb{<-} \hlkwd{combine}\hlstd{(hyperLOPIT2015ms3r1, hyperLOPIT2015ms3r2)}
\hlstd{combined}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 6725 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126.1 X127N.1 ... X131.2 (20 total)
##   varLabels: Replicate TMT.Reagent ... Iodixonal.Density (5 total)
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2Y3-3 (6725 total)
##   fvarLabels: EntryName ProteinDescription ... ProteinCoverage2 (8
##     total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
##   pubMedIds: 26754106 
## Annotation:  
## - - - Processing information - - -
## Combined [5489,10] and [6268,10] MSnSets Tue Apr 17 11:44:16 2018 
##  MSnbase version: 2.5.9
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{combined} \hlkwb{<-} \hlkwd{filterNA}\hlstd{(combined)}
\hlstd{combined}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 5032 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126.1 X127N.1 ... X131.2 (20 total)
##   varLabels: Replicate TMT.Reagent ... Iodixonal.Density (5 total)
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2R6 (5032 total)
##   fvarLabels: EntryName ProteinDescription ... ProteinCoverage2 (8
##     total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
##   pubMedIds: 26754106 
## Annotation:  
## - - - Processing information - - -
## Combined [5489,10] and [6268,10] MSnSets Tue Apr 17 11:44:16 2018 
## Subset [6725,20][5032,20] Tue Apr 17 11:44:17 2018 
## Removed features with more than 0 NAs: Tue Apr 17 11:44:17 2018 
## Dropped featureData's levels Tue Apr 17 11:44:17 2018 
##  MSnbase version: 2.5.9
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\subsection*{Features of interest}
In addition to adding annotation using the \texttt{addMarkers}
function, one can store specific sets of proteins by using the
\textit{Features of interest} infrastructure from the
\Biocpkg{MSnbase} package. If users have specific subsets of proteins
they wish to highlight in their data (possibly across multiple
experiments) they would first create a \texttt{FeaturesOfInterest}
object and then use the \textit{highlightOnPlot} function to
visualise these. For example, if we wanted to highlight
proteins with the accession numbers Q8CG48, Q8CG47, Q8K2Z4, and
Q8C156, which are some of the proteins known to form part of the
13S condensin complex, we would call the following code:

\begin{figure}[!ht]
  \centering
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{prots} \hlkwb{<-} \hlkwd{c}\hlstd{(}\hlstr{"Q8CG48"}\hlstd{,} \hlstr{"Q8CG47"}\hlstd{,} \hlstr{"Q8K2Z4"}\hlstd{,} \hlstr{"Q8C156"}\hlstd{)}
\hlstd{foi13s} \hlkwb{<-} \hlkwd{FeaturesOfInterest}\hlstd{(}\hlkwc{description} \hlstd{=} \hlstr{"13S consensin proteins"}\hlstd{,}
                             \hlkwc{fnames} \hlstd{= prots,}
                             \hlkwc{object} \hlstd{= hl)}
\hlstd{foi13s}
\end{alltt}
\begin{verbatim}
## Traceable object of class "FeaturesOfInterest"
##  Created on Tue Apr 17 11:44:19 2018 
##  Description:
##   13S consensin proteins
##  4 features of interest:
##    Q8CG48, Q8CG47, Q8K2Z4, Q8C156
\end{verbatim}
\begin{alltt}
\hlkwd{plot2D}\hlstd{(hl)}
\hlkwd{addLegend}\hlstd{(hl,} \hlkwc{cex} \hlstd{=} \hlnum{.6}\hlstd{)}
\hlkwd{highlightOnPlot}\hlstd{(hl, foi13s)}
\end{alltt}
\end{kframe}
\includegraphics[width=.8\textwidth]{figure/foi-1}

@@

% latex table generated in R 3.6.0 by xtable 1.8-2 package
% Tue Apr 17 11:44:19 2018
\begin{table}[ht]
\centering
\begin{tabular}{rrllr}
  \hline
 & Replicate & Tag & Gradient.Fraction & Iodixonal.Density \\ 
  \hline
X127C &   1 & 127C & 8 to 9 (pooled) & 11.00 \\ 
  X127C.1 &   2 & 127C & 7 to 9 (pooled) & 10.00 \\ 
   \hline
\end{tabular}
\caption{Differences in gradient fraction pooling.} 
\label{tab:pdtab}
\end{table}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{hl}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 5032 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126 X127N ... X131.1 (20 total)
##   varLabels: Replicate Tag Gradient.Fraction Iodixonal.Density
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2R6 (5032 total)
##   fvarLabels: uniprot.accession uniprot.id ... pd (27 total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
## Annotation:  
## - - - Processing information - - -
## Added markers from  'mrk' marker vector. Tue Apr 17 11:44:18 2018 
## Added markers from  'pdres' marker vector. Tue Apr 17 11:44:19 2018 
##  MSnbase version: 2.5.12
\end{verbatim}
\begin{alltt}
\hlkwd{getMarkers}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"pd"}\hlstd{)}
\end{alltt}
\begin{verbatim}
## organelleMarkers
##                          40S Ribosome 
##                                   106 
##                          60S Ribosome 
##                                    95 
## Endoplasmic reticulum/Golgi apparatus 
##                                   393 
##                         Mitochondrion 
##                                   525 
##                           Phenotype 1 
##                                   300 
##                           Phenotype 2 
##                                   253 
##                           Phenotype 3 
##                                   203 
##                           Phenotype 4 
##                                    74 
##                           Phenotype 5 
##                                    91 
##                       Plasma membrane 
##                                   421 
##                            Proteasome 
##                                    92 
##                               unknown 
##                                  2479
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{(ts} \hlkwb{<-} \hlkwd{orgQuants}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"svm"}\hlstd{,} \hlkwc{scol} \hlstd{=} \hlstr{"svm.scores"}\hlstd{,} \hlkwc{mcol} \hlstd{=} \hlstr{"markers"}\hlstd{,} \hlkwc{t} \hlstd{=} \hlnum{.5}\hlstd{))}
\end{alltt}
\begin{verbatim}
##            40S Ribosome            60S Ribosome      Actin cytoskeleton 
##               0.4368645               0.3031282               0.3889317 
##                 Cytosol   Endoplasmic reticulum                Endosome 
##               0.6760609               0.6075289               0.4353435 
##    Extracellular matrix                Lysosome           Mitochondrion 
##               0.4221860               0.5895546               0.9499026 
##     Nucleus - Chromatin Nucleus - Non-chromatin              Peroxisome 
##               0.7952921               0.7096399               0.3106030 
##         Plasma membrane              Proteasome 
##               0.7232975               0.4205260
##            40S Ribosome            60S Ribosome      Actin cytoskeleton 
##               0.4368645               0.3031282               0.3889317 
##                 Cytosol   Endoplasmic reticulum                Endosome 
##               0.6760609               0.6075289               0.4353435 
##    Extracellular matrix                Lysosome           Mitochondrion 
##               0.4221860               0.5895546               0.9499026 
##     Nucleus - Chromatin Nucleus - Non-chromatin              Peroxisome 
##               0.7952921               0.7096399               0.3106030 
##         Plasma membrane              Proteasome 
##               0.7232975               0.4205260
\end{verbatim}
\begin{alltt}
\hlstd{hl} \hlkwb{<-} \hlkwd{getPredictions}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"svm"}\hlstd{,} \hlkwc{scol} \hlstd{=} \hlstr{"svm.scores"}\hlstd{,} \hlkwc{mcol} \hlstd{=} \hlstr{"markers"}\hlstd{,} \hlkwc{t} \hlstd{= ts)}
\end{alltt}
\begin{verbatim}
## ans
##            40S Ribosome            60S Ribosome      Actin cytoskeleton 
##                      85                     171                      89 
##                 Cytosol   Endoplasmic reticulum                Endosome 
##                     299                     477                      99 
##    Extracellular matrix                Lysosome           Mitochondrion 
##                      27                     123                     521 
##     Nucleus - Chromatin Nucleus - Non-chromatin              Peroxisome 
##                     230                     343                      38 
##         Plasma membrane              Proteasome                 unknown 
##                     317                     156                    2057
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

## R Under development (unstable) (2018-04-02 r74505)

@@

## [1] stats4    parallel  stats     graphics  grDevices utils     datasets 
## [8] methods   base     

@@

##  [1] pRolocdata_1.17.3    pRoloc_1.19.4        MLInterfaces_1.59.1 
##  [4] cluster_2.0.7        annotate_1.57.3      XML_3.98-1.10       
##  [7] AnnotationDbi_1.41.4 IRanges_2.13.28      S4Vectors_0.17.41   
## [10] MSnbase_2.5.12       ProtGenerics_1.11.0  BiocParallel_1.13.3 
## [13] mzR_2.13.6           Rcpp_0.12.16         Biobase_2.39.2      
## [16] BiocGenerics_0.25.3  xtable_1.8-2         BiocStyle_2.7.8     

@@

##   [4] lazyeval_0.2.1        splines_3.6.0         ggvis_0.4.3          

@@

##  [10] foreach_1.4.4         BiocInstaller_1.29.6  htmltools_0.3.6      

@@

##  [19] limma_3.35.14         recipes_0.1.2         gower_0.1.2          

@@

##  [28] dplyr_0.7.4.9003      RCurl_1.95-4.10       hexbin_1.27.2        
##  [31] genefilter_1.61.1     bindr_0.1.1           impute_1.53.0        

@@

##  [40] zlibbioc_1.25.0       kernlab_0.9-25        ddalpha_1.3.1.1      
##  [43] prabclus_2.2-6        DEoptimR_1.0-8        scales_0.5.0         
##  [46] vsn_3.47.1            mvtnorm_1.0-7         DBI_0.8              
##  [49] viridisLite_0.3.0     progress_1.1.2        foreign_0.8-70       
##  [52] bit_1.1-12            proxy_0.4-22          mclust_5.4           
##  [55] preprocessCore_1.41.0 lava_1.6.1            prodlim_1.6.1        
##  [58] sampling_2.8          htmlwidgets_1.0       httr_1.3.1           
##  [61] threejs_0.3.1         FNN_1.1               RColorBrewer_1.1-2   
##  [64] fpc_2.1-11            modeltools_0.2-21     pkgconfig_2.0.1      
##  [67] flexmix_2.3-14        nnet_7.3-12           caret_6.0-78         
##  [70] tidyselect_0.2.4      rlang_0.2.0           reshape2_1.4.3       
##  [73] munsell_0.4.3         mlbench_2.1-1         tools_3.6.0          
##  [76] msdata_0.19.3         RSQLite_2.1.0         pls_2.6-0            
##  [79] broom_0.4.4           evaluate_0.10.1       stringr_1.3.0        
##  [82] mzID_1.17.0           yaml_2.1.18           ModelMetrics_1.1.0   
##  [85] bit64_0.9-7           robustbase_0.92-8     randomForest_4.6-14  
##  [88] purrr_0.2.4           dendextend_1.7.0      bindrcpp_0.2.2.9000  
##  [91] nlme_3.1-136          whisker_0.3-2         mime_0.5             
##  [94] RcppRoll_0.2.2        biomaRt_2.35.13       compiler_3.6.0       
##  [97] e1071_1.6-8           affyio_1.49.2         tibble_1.4.2         
## [100] stringi_1.1.7        
##  [ reached getOption("max.print") -- omitted 33 entries ]

>>>>

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{hl}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 5032 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData: none
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2R6 (5032 total)
##   fvarLabels: X X.1 ... Cell.Surface.Proteins (25 total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
## Annotation:  
## - - - Processing information - - -
##  MSnbase version: 2.4.2
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{combined} \hlkwb{<-} \hlkwd{combine}\hlstd{(hyperLOPIT2015ms3r1, hyperLOPIT2015ms3r2)}
\hlstd{combined}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 6725 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126.1 X127N.1 ... X131.2 (20 total)
##   varLabels: Replicate TMT.Reagent ... Iodixonal.Density (5 total)
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2Y3-3 (6725 total)
##   fvarLabels: EntryName ProteinDescription ... ProteinCoverage2 (8
##     total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
## Annotation:  
## - - - Processing information - - -
## Combined [6725,20] and [6268,10] MSnSets Tue Apr 17 13:59:46 2018 
##  MSnbase version: 1.21.7
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{combined} \hlkwb{<-} \hlkwd{filterNA}\hlstd{(combined)}
\hlstd{combined}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 5032 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126.1 X127N.1 ... X131.2 (20 total)
##   varLabels: Replicate TMT.Reagent ... Iodixonal.Density (5 total)
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2R6 (5032 total)
##   fvarLabels: EntryName ProteinDescription ... ProteinCoverage2 (8
##     total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
## Annotation:  
## - - - Processing information - - -
## Combined [6725,20] and [6268,10] MSnSets Tue Apr 17 13:59:46 2018 
## Subset [6725,20][5032,20] Tue Apr 17 13:59:47 2018 
## Removed features with more than 0 NAs: Tue Apr 17 13:59:47 2018 
## Dropped featureData's levels Tue Apr 17 13:59:47 2018 
##  MSnbase version: 1.21.7
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\subsection*{Features of interest}
In addition to adding annotation using the \texttt{addMarkers}
function, one can store specific sets of proteins by using the
\textit{Features of interest} infrastructure from the
\Biocpkg{MSnbase} package. If users have specific subsets of proteins
they wish to highlight in their data (possibly across multiple
experiments) they would first create a \texttt{FeaturesOfInterest}
object and then use the \textit{highlightOnPlot} function to
visualise these. For example, if we wanted to highlight
proteins with the accession numbers Q8CG48, Q8CG47, Q8K2Z4, and
Q8C156, which are some of the proteins known to form part of the
13S condensin complex, we would call the code displayed
on Figure \ref{fig:foi}. Users can also create several sets of \texttt{FeaturesOfInterest}
object and store them in a \texttt{FoICollection}.

\begin{figure}[!ht]
  \centering
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{prots} \hlkwb{<-} \hlkwd{c}\hlstd{(}\hlstr{"Q8CG48"}\hlstd{,} \hlstr{"Q8CG47"}\hlstd{,} \hlstr{"Q8K2Z4"}\hlstd{,} \hlstr{"Q8C156"}\hlstd{)}
\hlstd{foi13s} \hlkwb{<-} \hlkwd{FeaturesOfInterest}\hlstd{(}\hlkwc{description} \hlstd{=} \hlstr{"13S consensin proteins"}\hlstd{,}
                             \hlkwc{fnames} \hlstd{= prots,}
                             \hlkwc{object} \hlstd{= hl)}
\hlstd{foi13s}
\end{alltt}
\begin{verbatim}
## Traceable object of class "FeaturesOfInterest"
##  Created on Tue Apr 17 13:59:49 2018 
##  Description:
##   13S consensin proteins
##  4 features of interest:
##    Q8CG48, Q8CG47, Q8K2Z4, Q8C156
\end{verbatim}
\begin{alltt}
\hlkwd{plot2D}\hlstd{(hl)}
\hlkwd{addLegend}\hlstd{(hl,} \hlkwc{cex} \hlstd{=} \hlnum{.6}\hlstd{)}
\hlkwd{highlightOnPlot}\hlstd{(hl, foi13s)}
\end{alltt}
\end{kframe}
\includegraphics[width=.8\textwidth]{figure/foi-1}

@@

% latex table generated in R 3.4.4 by xtable 1.8-2 package
% Tue Apr 17 13:59:49 2018
\begin{table}[ht]
\centering
\begin{tabular}{rrllr}
  \hline
 & Replicate & Tag & Gradient.Fraction & Iodixonal.Density \\ 
  \hline
X127C &   1 & 127C & 8 to 9 (pooled) & 11.00 \\ 
  X127C.1 &   2 & 127C & 7 to 9 (pooled) & 10.00 \\ 
   \hline
\end{tabular}
\caption{Differences in gradient fraction pooling.} 
\label{tab:pdtab}
\end{table}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{hl}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 5032 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126 X127N ... X131.1 (20 total)
##   varLabels: Replicate Tag Gradient.Fraction Iodixonal.Density
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2R6 (5032 total)
##   fvarLabels: uniprot.accession uniprot.id ... pd (27 total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
## Annotation:  
## - - - Processing information - - -
## Added markers from  'mrk' marker vector. Tue Apr 17 13:59:48 2018 
## Added markers from  'pdres' marker vector. Tue Apr 17 13:59:49 2018 
##  MSnbase version: 2.4.2
\end{verbatim}
\begin{alltt}
\hlkwd{getMarkers}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"pd"}\hlstd{)}
\end{alltt}
\begin{verbatim}
## organelleMarkers
##                          40S Ribosome 
##                                   106 
##                          60S Ribosome 
##                                    95 
## Endoplasmic reticulum/Golgi apparatus 
##                                   393 
##                         Mitochondrion 
##                                   525 
##                           Phenotype 1 
##                                   300 
##                           Phenotype 2 
##                                   253 
##                           Phenotype 3 
##                                   203 
##                           Phenotype 4 
##                                    74 
##                           Phenotype 5 
##                                    91 
##                       Plasma membrane 
##                                   421 
##                            Proteasome 
##                                    92 
##                               unknown 
##                                  2479
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{(ts} \hlkwb{<-} \hlkwd{orgQuants}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"svm"}\hlstd{,} \hlkwc{scol} \hlstd{=} \hlstr{"svm.scores"}\hlstd{,} \hlkwc{mcol} \hlstd{=} \hlstr{"markers"}\hlstd{,} \hlkwc{t} \hlstd{=} \hlnum{.5}\hlstd{))}
\end{alltt}
\begin{verbatim}
##            40S Ribosome            60S Ribosome      Actin cytoskeleton 
##               0.4340512               0.3058889               0.3932999 
##                 Cytosol   Endoplasmic reticulum                Endosome 
##               0.6866550               0.6085893               0.4267912 
##    Extracellular matrix                Lysosome           Mitochondrion 
##               0.4088995               0.5917139               0.9495218 
##     Nucleus - Chromatin Nucleus - Non-chromatin              Peroxisome 
##               0.7946689               0.7107085               0.3134403 
##         Plasma membrane              Proteasome 
##               0.7229096               0.4193182
##            40S Ribosome            60S Ribosome      Actin cytoskeleton 
##               0.4340512               0.3058889               0.3932999 
##                 Cytosol   Endoplasmic reticulum                Endosome 
##               0.6866550               0.6085893               0.4267912 
##    Extracellular matrix                Lysosome           Mitochondrion 
##               0.4088995               0.5917139               0.9495218 
##     Nucleus - Chromatin Nucleus - Non-chromatin              Peroxisome 
##               0.7946689               0.7107085               0.3134403 
##         Plasma membrane              Proteasome 
##               0.7229096               0.4193182
\end{verbatim}
\begin{alltt}
\hlstd{hl} \hlkwb{<-} \hlkwd{getPredictions}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"svm"}\hlstd{,} \hlkwc{scol} \hlstd{=} \hlstr{"svm.scores"}\hlstd{,} \hlkwc{mcol} \hlstd{=} \hlstr{"markers"}\hlstd{,} \hlkwc{t} \hlstd{= ts)}
\end{alltt}
\begin{verbatim}
## ans
##            40S Ribosome            60S Ribosome      Actin cytoskeleton 
##                      85                     171                      89 
##                 Cytosol   Endoplasmic reticulum                Endosome 
##                     295                     477                      96 
##    Extracellular matrix                Lysosome           Mitochondrion 
##                      27                     125                     523 
##     Nucleus - Chromatin Nucleus - Non-chromatin              Peroxisome 
##                     229                     343                      38 
##         Plasma membrane              Proteasome                 unknown 
##                     317                     159                    2058
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

## R version 3.4.4 Patched (2018-03-19 r74516)

@@

## [1] stats4    parallel  methods   stats     graphics  grDevices utils    
## [8] datasets  base     

@@

##  [1] pRolocdata_1.16.0    pRoloc_1.18.0        MLInterfaces_1.58.1 
##  [4] cluster_2.0.7-1      annotate_1.56.2      XML_3.98-1.10       
##  [7] AnnotationDbi_1.40.0 IRanges_2.12.0       S4Vectors_0.16.0    
## [10] MSnbase_2.4.2        ProtGenerics_1.10.0  BiocParallel_1.12.0 
## [13] mzR_2.12.0           Rcpp_0.12.16         Biobase_2.38.0      
## [16] BiocGenerics_0.24.0  xtable_1.8-2         BiocStyle_2.6.1     

@@

##   [4] lazyeval_0.2.1        splines_3.4.4         ggvis_0.4.3          

@@

##  [10] foreach_1.4.4         BiocInstaller_1.28.0  htmltools_0.3.6      

@@

##  [19] limma_3.34.9          recipes_0.1.2         gower_0.1.2          

@@

##  [28] dplyr_0.7.4           RCurl_1.95-4.10       hexbin_1.27.2        
##  [31] genefilter_1.60.0     bindr_0.1.1           impute_1.52.0        

@@

##  [40] zlibbioc_1.24.0       kernlab_0.9-25        ddalpha_1.3.2        
##  [43] prabclus_2.2-6        DEoptimR_1.0-8        abind_1.4-5          
##  [46] scales_0.5.0.9000     vsn_3.46.0            mvtnorm_1.0-7        
##  [49] DBI_0.8               viridisLite_0.3.0     progress_1.1.2       
##  [52] magic_1.5-8           foreign_0.8-69        bit_1.1-12           
##  [55] proxy_0.4-22          mclust_5.4            preprocessCore_1.40.0
##  [58] lava_1.6.1            prodlim_1.6.1         sampling_2.8         
##  [61] htmlwidgets_1.0       httr_1.3.1            threejs_0.3.1        
##  [64] FNN_1.1               RColorBrewer_1.1-2    fpc_2.1-11           
##  [67] modeltools_0.2-21     pkgconfig_2.0.1       flexmix_2.3-14       
##  [70] nnet_7.3-12           caret_6.0-79          tidyselect_0.2.4     
##  [73] rlang_0.2.0           reshape2_1.4.3        munsell_0.4.3        
##  [76] mlbench_2.1-1         tools_3.4.4           msdata_0.18.0        
##  [79] RSQLite_2.1.0         pls_2.6-0             broom_0.4.4          
##  [82] evaluate_0.10.1       geometry_0.3-6        stringr_1.3.0        
##  [85] mzID_1.16.0           yaml_2.1.18           ModelMetrics_1.1.0   
##  [88] bit64_0.9-7           robustbase_0.92-8     randomForest_4.6-14  
##  [91] purrr_0.2.4           dendextend_1.7.0      bindrcpp_0.2.2       
##  [94] nlme_3.1-137          whisker_0.3-2         mime_0.5             
##  [97] RcppRoll_0.2.2        biomaRt_2.34.2        compiler_3.4.4       
## [100] e1071_1.6-8          
##  [ reached getOption("max.print") -- omitted 37 entries ]
